PANCHANGE_variable_creation

### 2020-11-20 PANCHANGE_exclusion_descriptives.Rmd
knitted all scripts

---
title: "PANCHANGE_descriptives"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: Sys.Date()
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

>>>>

---
title: "PANCHANGE_descriptives"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

### 2020-11-20 PANCHANGE_variable_creation.Rmd
knitted all scripts

---
title: "PANCHANGE_variable_creation"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: Sys.Date()
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

>>>>

---
title: "PANCHANGE_variable_creation"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show
